---
title: "EoI Reviews by TRC"
output:
  html_document:
    df_print: paged
  flexdashboard::flex_dashboard:
    orientation: rows
    social: menu
    source_code: embed
  word_document: default
  pdf_document: default
---
<style type="text/css">
.main-container {
  max-width: 1300px;
  margin-left: auto;
  margin-right: auto;
}
</style>
<style type="text/css">

body{ /* Normal  */
      font-size: 14px;
  }
td {  /* Table  */
  font-size: 14px;
}
h1.title {
  font-size: 38px;
}
h1 { /* Header 1 */
  font-size: 28px;
}
h2 { /* Header 2 */
    font-size: 22px;
}
h3 { /* Header 3 */
    font-size: 18px;
}
code.r{ /* Code block */
    font-size: 12px;
}
pre { /* Code block - determines code spacing between lines */
    font-size: 14px;
}
</style>


```{r, echo=FALSE}
suppressWarnings(suppressPackageStartupMessages(library(ggplot2)))
suppressWarnings(suppressPackageStartupMessages(library(dplyr)))
suppressWarnings(suppressPackageStartupMessages(library(leaflet)))
suppressWarnings(suppressPackageStartupMessages(library(DT)))
suppressWarnings(suppressPackageStartupMessages(library(stringr)))
suppressWarnings(suppressPackageStartupMessages(library(knitr)))
suppressWarnings(suppressPackageStartupMessages(library(markdown)))
suppressWarnings(suppressPackageStartupMessages(library(rmarkdown)))
suppressWarnings(suppressPackageStartupMessages(library(crosstalk)))
suppressWarnings(suppressPackageStartupMessages(library(reactable)))
suppressWarnings(suppressPackageStartupMessages(library(plotly)))
suppressWarnings(suppressPackageStartupMessages(library(flexdashboard)))


setwd("C:/Users/MichaelOwen/Documents/Tinkering/ICI/Markdown")

```

```{r, echo=FALSE}
fullData <- readxl::read_xlsx("fulldata.xlsx")
fullData <- fullData[9:10,]

```

\AtBeginDocument{\let\maketitle\relax}


# Assessment of EoI:`r fullData$EoI[1]` 

<br><br>

# EoI Metadata
```{r echo = FALSE}

full_Data <- SharedData$new(fullData[c(1,4:7,26,49,62,65)])
  reactable(full_Data,
            minRows = 0,
            highlight = TRUE,
            striped = TRUE)

```

### Performance of EoI `r fullData$EoI[1]` in Key Geography - Percentile by Average Score

```{r echo = FALSE}
summaryStats <- read.csv("congoSummaryStats.csv")

data <- SharedData$new(summaryStats)

p <- ggplot(data, aes(x=Average, y=Percentile, color = Geography), group = EoI) +
            geom_point(shape=1)





bscols(
  widths = c(8),
ggplotly(p)
)
```


***

### **Section 1 - Experience & strengths relevant to the proposed Indigenous territory, landscape/seascape (Total Points: 30)**

[A) Importance of the landscape/seascape/indigenous territory for
biodiversity, with additional consideration to climate benefits.]{.ul}

1\. Is the proposed territory/landscape/seascape a globally important
area for biodiversity?

*Scoring:*

-   Not significant;

-   Low Significance;

-   Moderate Significance;

-   Medium-high Significance;

-   High Significance;

-   Exceptional Significance

##### *Reviewer A:* `r fullData$Section1_A1[1]`/5   *Reviewer B:* `r fullData$Section1_A1[2]`/5
#### **Average: `r mean(fullData$Section1_A1)`/5**


*Evidence A:* `r fullData$Evidence1_A1[1]` 

*Evidence B:*`r fullData$Evidence1_A1[2]` 

<br>

2\. Is the area important for climate mitigation?

*Scoring:*

-   \>50 t/ha - Low;

-   50 - 100 t/ha - Moderate;

-   \>100 t/ha - High

##### *Reviewer A:* `r fullData$Section1_A2[1]`/2   *Reviewer B:* `r fullData$Section1_A2[2]`/2
#### **Average: `r mean(fullData$Section1_A2)`/2**


*Evidence A:* `r fullData$Evidence1_A2[1]` 

*Evidence B:*`r fullData$Evidence1_A2[2]` 

<br>

[B) Geographical focus in an area under IPLC governance.]{.ul}

3\. Is the area held and managed by IPLC under community-based
governance systems?

*Scoring:*

-   IPLC governance (rights and institutions) not evident;

-   Project areas are marginally under IPLC governance (spatially or
    politically);

-   Project areas are partially under IPLC systems of governance
    (spatially or politically);

-   Project areas are largely under IPLC governance, but IPLC rights
    and/or institutions face significant constraints;

-   Project areas are held and managed under IPLC governance systems,
    with some limitations;

-   Project areas are held and managed under strong and active IPLC
    governance systems

##### *Reviewer A:* `r fullData$Section1_B3[1]`/5   *Reviewer B:* `r fullData$Section1_B3[2]`/5
#### **Average: `r mean(fullData$Section1_B3)`/5**


*Evidence A:* `r fullData$Evidence1_B3[1]` 

*Evidence B:*`r fullData$Evidence1_B3[2]` 

<br>

4\. Does the proposal explain the unique cultural significance of the
area to IPLCs?

*Scoring:*

-   No explanation given of unique significance to IPLCs;

-   Significance of site(s) vaguely described;

-   Unique significance of project site(s) clearly explained

##### *Reviewer A:* `r fullData$Section1_B4[1]`/2   *Reviewer B:* `r fullData$Section1_B4[2]`/2
#### **Average: `r mean(fullData$Section1_B4)`/2**


*Evidence A:* `r fullData$Evidence1_B4[1]` 

*Evidence B:*`r fullData$Evidence1_B4[2]` 

<br>


[C) Vulnerability of the proposed IPLCs as well as their
lands/waters/natural resources to threats.]{.ul}

5\. Is the area vulnerable to threats/current risk of negative impacts
to IPLC and biodiversity without action?

*Scoring:*

-   No evident threats;

-   Low threats;

-   Moderate threats;

-   Medium-high threats;

-   High threats;

-   Requires urgent action

##### *Reviewer A:* `r fullData$Section1_C5[1]`/5   *Reviewer B:* `r fullData$Section1_C5[2]`/5
#### **Average: `r mean(fullData$Section1_C5)`/5**


*Evidence A:* `r fullData$Evidence1_C5[1]` 

*Evidence B:*`r fullData$Evidence1_C5[2]` 

<br>

[D) Opportunities for ICI results - including enabling policy
conditions, positive government support and presence of successful
IPLC-led conservation initiatives that could be scaled up.]{.ul}

6\. Are enabling policy conditions in place for IPLC-led conservation in
the proposed area?

*Scoring:*

-   Legal and policy frameworks in project areas undermine IPLC
    governance (either actively or through absence);

-   Legal and policy frameworks recognize limited rights for IPLCs over
    their lands and/or resources;

-   Legal and policy frameworks recognize rights over lands and
    resources but with constraints (e.g., lack implementing
    regulations);

-   Legal and policy frameworks actively promote the recognition of IPLC
    governance

##### *Reviewer A:* `r fullData$Section1_D6[1]`/3   *Reviewer B:* `r fullData$Section1_D6[2]`/3
#### **Average: `r mean(fullData$Section1_D6)`/3**


*Evidence A:* `r fullData$Evidence1_D6[1]` 

*Evidence B:*`r fullData$Evidence1_D6[2]` 

<br>

7\. Is there active government support for IPLC-led conservation in the
proposed country/area?

*Scoring:*

-   National or sub-national governments are actively opposed to
    IPLC-led conservation;

-   National or sub-national governments have recognized the importance
    of IPLC-led conservation;

-   National or sub-national governments have implemented some support
    for IPLC-led conservation;

-   National or sub-national governments are actively engaged in the
    promotion of IPLC rights and IPLC-led conservation

##### *Reviewer A:* `r fullData$Section1_D7[1]`/3   *Reviewer B:* `r fullData$Section1_D7[2]`/3
#### **Average: `r mean(fullData$Section1_D7)`/3**


*Evidence A:* `r fullData$Evidence1_D7[1]` 

*Evidence B:*`r fullData$Evidence1_D7[2]` 

<br>


8\. Are there successful IPLC-led conservation initiatives in the
proposed area that provide a foundation for scaling up?

*Scoring:*

-   No IPLC-led conservation initiatives have been implemented;

-   Few IPLC-led conservation projects have been implemented in pilot
    stages only;

-   Some IPLC-led conservation projects have been implemented beyond
    pilot stages;

-   Relevant IPLC-led conservation projects have been well established
    for many years

##### *Reviewer A:* `r fullData$Section1_D8[1]`/3   *Reviewer B:* `r fullData$Section1_D8[2]`/3
#### **Average: `r mean(fullData$Section1_D8)`/3**


*Evidence A:* `r fullData$Evidence1_D8[1]` 

*Evidence B:*`r fullData$Evidence1_D8[2]` 

<br>

[E) Synergies with existing investments.]{.ul}

9\. Are there other initiatives (relevant projects) that provide
complementary support for IPLC-led conservation in the geography?

*Scoring:*

-   Few to no complementary projects/investment;

-   Complementary projects/investments are small, or are tangentially
    related to project goals;

-   Complementary Projects/investments align strongly with project goals
    and investments are substantial


##### *Reviewer A:* `r fullData$Section1_E9[1]`/2   *Reviewer B:* `r fullData$Section1_E9[2]`/3
#### **Average: `r mean(fullData$Section1_E9)`/2**


*Evidence A:* `r fullData$Evidence1_E9[1]` 

*Evidence B:*`r fullData$Evidence1_E9[2]` 

<br>
<br>

## **Section 1:**
##### *Reviewer A Total Score:* `r fullData$Section1_Total[1]`/30   
##### *Reviewer B Total Score:* `r fullData$Section1_Total[2]`/30  

#### **Average Total Score: `r mean(fullData$Section1_Total)`/30**

<br>
<br>


***
**Section 2 - Quality and ability of the proposed approach and
interventions to achieve transformational impact that generate the
global environmental benefits (Total Points: 40)**

[A) Quality of proposed approach and ability to support traditional
structures, knowledge and community practices in the delivery of global
environmental benefits.]{.ul}

1\. Is the proposed approach well aligned with the overall objective of
the ICI to: Enhance Indigenous Peoples\' and Local Communities\' (IPLCs)
efforts to steward land, waters and natural resources to deliver global
environmental benefits?

*Scoring:*

-   Weakly aligned;

-   Partially aligned;

-   Well aligned;

-   Exceptionally well aligned

##### *Reviewer A:* `r fullData$Section2_A1[1]`/3   *Reviewer B:* `r fullData$Section2_A1[2]`/3
#### **Average: `r mean(fullData$Section2_A1)`/3**


*Evidence A:* `r fullData$Evidence2_A1[1]` 

*Evidence B:*`r fullData$Evidence2_A1[2]` 

<br>

2\. Does the EoI present a clear and convincing set of activities and
results?

*Scoring:*

-   The objectives and approach for this project lack clarity and
    cohesion, and/or do not appear to be realistic for the context;

-   Activities & results defined but logic (Theory of Change) is
    incomplete;

-   Activities and results are well-defined and cohesive but some
    aspects require clarification;

-   The project has clear objectives and a cohesive approach with
    relevant activities for the context and timeline

##### *Reviewer A:* `r fullData$Section2_A2[1]`/6   *Reviewer B:* `r fullData$Section2_A2[2]`/6
#### **Average: `r mean(fullData$Section2_A2)`/6**


*Evidence A:* `r fullData$Evidence2_A2[1]` 

*Evidence B:*`r fullData$Evidence2_A2[2]` 

<br>

3\. Will the project (objectives and activities) contribute to
overcoming identified threats and putting in place necessary enabling
opportunities for IPLC-led conservation?

*Scoring:*

-   Objectives and activities do not clearly address identified threats
    and opportunities;

-   Contributions to addressing the threats and opportunities are low;

-   Contributions to addressing threats and enabling conditions are
    slightly over-ambitious;

-   The impact on threats and enabling conditions can be realistically
    accomplished and are sufficiently ambitious for the projects\'
    context

##### *Reviewer A:* `r fullData$Section2_A3[1]`/3   *Reviewer B:* `r fullData$Section2_A3[2]`/3
#### **Average: `r mean(fullData$Section2_A3)`/3**


*Evidence A:* `r fullData$Evidence2_A3[1]` 

*Evidence B:*`r fullData$Evidence2_A3[2]` 

<br>

4\. Are the activities achievable within a \$500,000 to \$2,000,000 USD
budget range in a period of 5 years of project execution?

*Scoring:*

-   Activities/results not aligned with EoI range of investment;

-   Activities/results Partially aligned with EoI range of investment ;

-   Activities/results Well aligned with EoI range of investment ;

-   Activities/results Exceptionally well aligned with EoI range of
    investment

##### *Reviewer A:* `r fullData$Section2_A4[1]`/3   *Reviewer B:* `r fullData$Section2_A4[2]`/3
#### **Average: `r mean(fullData$Section2_A4)`/3**


*Evidence A:* `r fullData$Evidence2_A4[1]` 

*Evidence B:*`r fullData$Evidence2_A4[2]` 

<br>

5\. Does the EoI include significant and concrete sources of
co-financing?

*Scoring:*

-   None;

-   Small;

-   Moderate;

-   Significant

##### *Reviewer A:* `r fullData$Section2_A5[1]`/3   *Reviewer B:* `r fullData$Section2_A5[2]`/3
#### **Average: `r mean(fullData$Section2_A5)`/3**


*Evidence A:* `r fullData$Evidence2_A5[1]` 

*Evidence B:*`r fullData$Evidence2_A5[2]` 

<br>

[B) Potential of the proposed activities to achieve IPLC-led
transformational impact that generate global environmental
benefits.]{.ul}

6\. Are the estimated Global Environmental Benefits (GEF core
indicators) substantial and realistic?

*Scoring:*

-   Not provided;

-   Very Low (below 10,000 Ha);

-   Moderate (between 100,000 - 500,000 Ha);

-   High (between 500,000 - 1,000,000 Ha);

-   Very high above 1,000,000 Ha

##### *Reviewer A:* `r fullData$Section2_B6[1]`/5   *Reviewer B:* `r fullData$Section2_B6[2]`/5
#### **Average: `r mean(fullData$Section2_B6)`/5**


*Evidence A:* `r fullData$Evidence2_B6[1]` 

*Evidence B:*`r fullData$Evidence2_B6[2]` 

<br>

7\. Are the additional cultural and livelihoods results contributing to
project objectives?

*Scoring:*

-   No provided cultural or livelihood indicators for the project;

-   Indicators proposed but are not clearly aligned with project goals;

-   Indicators proposed and are moderately aligned with project goals;

-   Additional cultural and/or livelihood indicators clearly derive from
    project goals

##### *Reviewer A:* `r fullData$Section2_B7[1]`/3   *Reviewer B:* `r fullData$Section2_B7[2]`/3
#### **Average: `r mean(fullData$Section2_B7)`/3**


*Evidence A:* `r fullData$Evidence2_B7[1]` 

*Evidence B:*`r fullData$Evidence2_B7[2]` 

<br>

8\. Does the EoI provide a clear and robust vision for long-term
sustainability?

*Scoring:*

-   Vision for long-term sustainability not provided;

-   This project does not seem to have a clear long-term impact;

-   This project will create medium-term benefits for biodiversity and
    IPLC governance, which future funding will hopefully build upon;

-   This project will ensure long-term benefits to biodiversity and IPLC
    systems of governance

##### *Reviewer A:* `r fullData$Section2_B8[1]`/3   *Reviewer B:* `r fullData$Section2_B8[2]`/3
#### **Average: `r mean(fullData$Section2_B8)`/3**


*Evidence A:* `r fullData$Evidence2_B8[1]` 

*Evidence B:*`r fullData$Evidence2_B8[2]` 

<br>

[C) IPLC-led conservation that advances national and global
environmental priorities.]{.ul}

9\. Does the EoI build on and contribute to national priorities as
defined in NBSAPs and/or NDCs?

*Scoring:*

-   Contributions not provided;

-   The project is weakly related to either national priorities;

-   The project appears to be tangentially related to national
    priorities;

-   The proposal reflects an understanding of the national policy
    priorities and clearly positions the project in relation to those
    priorities

##### *Reviewer A:* `r fullData$Section2_C9[1]`/3   *Reviewer B:* `r fullData$Section2_C9[2]`/3
#### **Average: `r mean(fullData$Section2_C9)`/3**


*Evidence A:* `r fullData$Evidence2_C9[1]` 

*Evidence B:*`r fullData$Evidence2_C9[2]` 

<br>

[D) Demonstrated gender mainstreaming in all activities.]{.ul}

10\. Does the EoI provide a clear and robust approach to gender
mainstreaming?

*Scoring:*

-   Gender mainstreaming approach is absent;

-   Gender mainstreaming approach is weak;

-   Gender mainstreaming approach is moderately thought through (if
    there are a few activities as \'add ons\');

-   Significant and well-thought through approach to gender
    mainstreaming

##### *Reviewer A:* `r fullData$Section2_D10[1]`/3   *Reviewer B:* `r fullData$Section2_D10[2]`/3
#### **Average: `r mean(fullData$Section2_D10)`/3**


*Evidence A:* `r fullData$Evidence2_D10[1]` 

*Evidence B:*`r fullData$Evidence2_D10[2]` 

<br>

[E) Innovation and potential to scale up.]{.ul}

11\. Do the proposed activities and results demonstrate innovation and
potential for transformative results at scale?

*Scoring:*

-   None demonstrated;

-   Low demonstrated potential;

-   Moderate demonstrated potential;

-   Medium-high demonstrated potential;

-   High demonstrated potential;

-   Exceptional demonstrated potential

##### *Reviewer A:* `r fullData$Section2_E11[1]`/5   *Reviewer B:* `r fullData$Section2_E11[2]`/5
#### **Average: `r mean(fullData$Section2_E11)`/5**


*Evidence A:* `r fullData$Evidence2_E11[1]` 

*Evidence B:*`r fullData$Evidence2_E11[2]` 

<br>
<br>

## **Section 2:**
##### *Reviewer A Total Score:* `r fullData$Section2_Total[1]`/40   
##### *Reviewer B Total Score:* `r fullData$Section2_Total[2]`/40  

#### **Average Total Score: `r mean(fullData$Section2_Total)`/40**

<br>
<br>



***
**Section 3 - Qualifications and experience of the Organization (Total
Points: 30)**

[A) Indigenous Peoples or Local Community organization legally
recognized under national laws.]{.ul}

1\. Is the EoI led by an IPLC organization?

*Scoring:*

-   IPLC appear to be beneficiaries only;

-   Combination/partnership of IPLC organizations and NGOs, and plans to
    build IPLC capacity over the project term are clear;

-   IPLC-led approach, NGOs in more limited, defined roles (such as
    fiduciary);

-   Fully IPLC composed and led approach

##### *Reviewer A:* `r fullData$Section3_A1[1]`/6   *Reviewer B:* `r fullData$Section3_A1[2]`/6
#### **Average: `r mean(fullData$Section3_A1)`/6**


*Evidence A:* `r fullData$Evidence3_A1[1]` 

*Evidence B:*`r fullData$Evidence3_A1[2]` 

<br>

[B) Demonstrated on the ground leadership related to Indigenous Peoples
and/or Local Community Conservation.]{.ul}

2\. Does the lead proponent demonstrate on-ground leadership relevant to
the proposed work?

*Scoring:*

-   None demonstrated;

-   Limited demonstration of relevant on-ground leadership;

-   Demonstrated on-ground leadership relevant to the proposed work;

-   Exceptional and long-standing on-ground leadership relevant to the
    proposed work

##### *Reviewer A:* `r fullData$Section3_B2[1]`/6   *Reviewer B:* `r fullData$Section3_B2[2]`/6
#### **Average: `r mean(fullData$Section3_B2)`/6**


*Evidence A:* `r fullData$Evidence3_B2[1]` 

*Evidence B:*`r fullData$Evidence3_B2[2]` 

<br>

[C) Proven relevant experience in working with IPLC networks, alliances
and organizations/ strength of partnerships on the ground.]{.ul}

3\. Does EoI demonstrate that the lead proponent has strong
partnerships, particularly with other IPLC organizations, to carry out
the work?

*Scoring:*

-   No partners defined;

-   No IPLC partners identified;

-   IPLC organizations are listed as implementing partners but without
    clear scope (roles in project design or governance);

-   IPLC organizations are listed as implementing partners with clear
    roles (in project design or governance);

-   Strong IPLC partnerships that play a central role in design,
    governance, and implementation of the project;

-   Strong IPLC partnerships have a central role in design, governance
    and implementation of the project and linkages with national or
    regional IPO networks

##### *Reviewer A:* `r fullData$Section3_C3[1]`/5   *Reviewer B:* `r fullData$Section3_C3[2]`/5
#### **Average: `r mean(fullData$Section3_C3)`/5**


*Evidence A:* `r fullData$Evidence3_C3[1]` 

*Evidence B:*`r fullData$Evidence3_C3[2]` 

<br>

[D) Technical expertise and capacity to address environmental problems,
root causes and barriers.]{.ul}

4\. Does EoI demonstrate technical capacity of lead proponent and
partners to deliver the proposed results?

*Scoring:*

-   No skills demonstrated;

-   The skills and experiences outlined have little or no relation to
    the project activities;

-   There is some lack of clarity or some gaps in the capacities
    necessary to implement the project;

-   The activities clearly show how they plan to fill capacity gaps over
    the course of the project;

-   They seem to have adequate skills and capacity for the project but
    do not have experience with GEF projects;

-   The lead organization and project partners clearly communicate that
    they have all the skills and experience necessary to implement the
    project activities. Also, have past experience with GEF funded
    projects.

##### *Reviewer A:* `r fullData$Section3_D4[1]`/5   *Reviewer B:* `r fullData$Section3_D4[2]`/5
#### **Average: `r mean(fullData$Section3_D4)`/5**


*Evidence A:* `r fullData$Evidence3_D4[1]` 

*Evidence B:*`r fullData$Evidence3_D4[2]` 

<br>

[E) Project Management capacity.]{.ul}

5\. Does the EoI demonstrate project & financial management capacity
needed for scale of proposed effort?

*Scoring:*

-   Very limited (no criteria met);

-   Some capacity but would require support (1/3 criteria);

-   Moderate capacity (2/3 criteria met);

-   Very strong (all criteria met) with demonstrated past performance

##### *Reviewer A:* `r fullData$Section3_E5[1]`/6   *Reviewer B:* `r fullData$Section3_E5[2]`/6
#### **Average: `r mean(fullData$Section3_E5)`/6**


*Evidence A:* `r fullData$Evidence3_E5[1]` 

*Evidence B:*`r fullData$Evidence3_E5[2]` 

<br>

6\. Does lead organization have experience with safeguards and other
standards required by GEF?

*Scoring:*

-   Answered no;

-   Answered yes but with weak or lacking explanation to the extent;

-   Answered yes with clear explanation of the extent

##### *Reviewer A:* `r fullData$Section3_E6[1]`/2   *Reviewer B:* `r fullData$Section3_E6[2]`/2
#### **Average: `r mean(fullData$Section3_E6)`/2**


*Evidence A:* `r fullData$Evidence3_E6[1]` 

*Evidence B:*`r fullData$Evidence3_E6[2]` 

<br>
<br>

## **Section 3:**
##### *Reviewer A Total Score:* `r fullData$Section3_Total[1]`/30   
##### *Reviewer B Total Score:* `r fullData$Section3_Total[2]`/30  

#### **Average Total Score: `r mean(fullData$Section2_Total)`/30**

<br>
<br>
