---
title: "Overview of EoI Reviews by TRC"
output:
  html_document:
    df_print: paged
  flexdashboard::flex_dashboard:
    orientation: rows
    social: menu
    source_code: embed
  pdf_document: default
  word_document: default

---
<style type="text/css">
.main-container {
  max-width: 1800px;
  margin-left: auto;
  margin-right: auto;
}
</style>




```{r setup, include=FALSE}
library(ggplot2)
library(crosstalk)
library(reactable)
library(plotly)
library(plyr)
library(flexdashboard)
library(htmltools)

```

-----------------------------------------------------------------------
### Summary Data of all reviews, aggregated by EoI
##### Use the controls on the left to subset the summary table and plot that follows.
##### Select a link in the EoI column to open the respective detailed report in a new tab.


```{r echo = FALSE}

summaryStats <- read.csv("/Users/MichaelOwen/Documents/Github/ICIReview/docs/summaryStats_Round.csv")
data <- SharedData$new(summaryStats)

bscols(
  widths = c(3, 9),
  list(
    filter_checkbox("Geography", "Geography", data, ~Geography),
    filter_slider("average", "Average", data, ~Average, width = "100%"),
    filter_select("EoI", "EoI Number", data, ~EoI)
  ),
  reactable(data, 
            columns = list(
  
    EoI = colDef(html = TRUE, cell = function(value, index) {
    # Render as a link
    url <- paste0("report.", value,".html")
    htmltools::tags$a(href = url, target = "_blank", as.character(value))
  }),
  
    Geography = colDef(minWidth = 115 ,cell = function(value) {
    if (value == "Melanesia/Polynesia") "Melanesia/ Polynesia" else
    value
  }),
    nReviews = colDef(minWidth = 85, name = "# of Reviews", html = TRUE, align = "left", header = JS("
      function(colInfo) {
        return colInfo.column.name
      }
    ")),
    Average = colDef(minWidth = 85),
    Avg_Sec_1 = colDef(minWidth = 85, name = "Average Section 1", html = TRUE, align = "left", header = JS("
      function(colInfo) {
        return colInfo.column.name
      }
    ")),
    Avg_Sec_2 = colDef(minWidth = 85, name = "Average Section 2", html = TRUE, align = "left", header = JS("
      function(colInfo) {
        return colInfo.column.name
      }
    ")),
    Avg_Sec_3 = colDef(minWidth = 85, name = "Average Section 3", html = TRUE, align = "left", header = JS("
      function(colInfo) {
        return colInfo.column.name
      }
    ")),
    Total = colDef(minWidth = 60),
    Min = colDef(minWidth = 60),
    Max = colDef(minWidth = 60),
    Range = colDef(minWidth = 60),
    Geog_Percentile = colDef(minWidth = 85, name = "Geog. Percentile", html = TRUE, align = "left", header = JS("
      function(colInfo) {
        return colInfo.column.name + '<div style=\"color: #999\">(%)</div>'
      }
    ")),
    Geog_Rank = colDef(minWidth = 75, name = "Geog. Rank", html = TRUE, align = "left", header = JS("
      function(colInfo) {
        return colInfo.column.name
      }
    ")),
    Overall_Rank = colDef(minWidth = 75, name = "Overall Rank", html = TRUE, align = "left", header = JS("
      function(colInfo) {
        return colInfo.column.name
      }
    ")),
    Overall_Percentile = colDef(minWidth = 85, name = "Overall Percentile", html = TRUE, align = "left", header = JS("
      function(colInfo) {
        return colInfo.column.name + '<div style=\"color: #999\">(%)</div>'
      }
    "))),
    showPageSizeOptions = TRUE, pageSizeOptions = c(5, 10, 25, 50), defaultPageSize = 5,
    defaultSorted = list(Average = "desc"),
            highlight = TRUE,
            striped = TRUE)

)
```

<P style="page-break-before: always;">
### Performance of EoIs - Percentile by Average Total Score

```{r echo = FALSE}
p <- ggplot(data, aes(x=Average, y=Geog_Percentile, color = Geography, text=paste0("EoI: ", EoI,
                                                                                  "<br>",
                                                                                  "Geography: ", Geography,
                                                                                  "<br>",
                                                                                  "Average: ", Average,
                                                                                  "<br>",
                                                                                  "Geog. Percentile: ", Geog_Percentile)),
            group = Geography) +
            geom_point(position=position_dodge2(width = 0.01, preserve = "single"),
             shape = 1, alpha = 0.9) +
            xlab("Average Total Score") +
            ylab("Geography Overall Percentile") +
            scale_x_continuous(limits = c(0, 100)) +
            scale_y_continuous(limits = c(0, 1)) +
            labs(color = "EoIs")
          




bscols(
  widths = c(8),
ggplotly(p, tooltip="text") %>%
      config(displaylogo = FALSE, 
             toImageButtonOptions = list(
               format = "png",
               filename = paste0("Overall"),
               width = 600,
               height = 600
             ),
             modeBarButtonsToRemove = c(
               'sendDataToCloud',
               'select2d',
               'autoScale2d',
               'lasso2d',
               'zoomIn2d',
               'zoomOut2d',
               'pan2d'
             )) %>%
      layout(autosize = TRUE, margin = list(t = 50))
)
```

<P style="page-break-before: always;">
### Performance of EoIs - Percentile by Average Score (Section 1)

```{r echo = FALSE}


p <- ggplot(data, aes(x=Avg_Sec_1, y=Geog_Percentile, color = Geography, text=paste0("EoI: ", EoI,
                                                                                  "<br>",
                                                                                  "Geography: ", Geography,
                                                                                  "<br>",
                                                                                  "Average: ", Average,
                                                                                  "<br>",
                                                                                  "Geog. Percentile: ", Geog_Percentile)), group = EoI) +
            geom_point(position=position_dodge2(width = 0.01, preserve = "single"),
             shape = 1, alpha = 0.9) +
          xlab("Average Section 1") +
          ylab("Geography Overall Percentile") +
          scale_x_continuous(limits = c(0, 30)) +
          scale_y_continuous(limits = c(0, 1)) +
          labs(color = "EoIs")
        



bscols(
  widths = c(8),
ggplotly(p, tooltip="text") %>%
      config(displaylogo = FALSE, 
             toImageButtonOptions = list(
               format = "png",
               filename = paste0("Section1"),
               width = 600,
               height = 600
             ),
             modeBarButtonsToRemove = c(
               'sendDataToCloud',
               'select2d',
               'autoScale2d',
               'lasso2d',
               'zoomIn2d',
               'zoomOut2d',
               'pan2d'
             )) %>%
      layout(autosize = TRUE, margin = list(t = 50))
)
```

<P style="page-break-before: always;">
### Performance of EoIs - Percentile by Average Score (Section 2)

```{r echo = FALSE}


p <- ggplot(data, aes(x=Avg_Sec_2, y=Geog_Percentile, color = Geography, text=paste0("EoI: ", EoI,
                                                                                  "<br>",
                                                                                  "Geography: ", Geography,
                                                                                  "<br>",
                                                                                  "Average: ", Average,
                                                                                  "<br>",
                                                                                  "Geog. Percentile: ", Geog_Percentile)), group = EoI) +
            geom_point(position=position_dodge2(width = 0.01, preserve = "single"),
             shape = 1, alpha = 0.9) +
            xlab("Average  Section 2") +
            ylab("Geography Overall Percentile") +
            scale_x_continuous(limits = c(0, 40)) +
            scale_y_continuous(limits = c(0, 1)) +
            labs(color = "EoIs")
          
          


bscols(
  widths = c(8),
ggplotly(p, tooltip="text") %>%
      config(displaylogo = FALSE, 
             toImageButtonOptions = list(
               format = "png",
               filename = paste0("Section2"),
               width = 600,
               height = 600
             ),
             modeBarButtonsToRemove = c(
               'sendDataToCloud',
               'select2d',
               'autoScale2d',
               'lasso2d',
               'zoomIn2d',
               'zoomOut2d',
               'pan2d'
             )) %>%
      layout(autosize = TRUE, margin = list(t = 50))
)
```

<P style="page-break-before: always;">
### Performance of EoIs - Percentile by Average Score (Section 3)

```{r echo = FALSE}



p <- ggplot(data, aes(x=Avg_Sec_3, y=Geog_Percentile, color = Geography, text=paste0("EoI: ", EoI,
                                                                                  "<br>",
                                                                                  "Geography: ", Geography,
                                                                                  "<br>",
                                                                                  "Average: ", Average,
                                                                                  "<br>",
                                                                                  "Geog. Percentile: ", Geog_Percentile)), group = EoI) +
            geom_point(position=position_dodge2(width = 0.01, preserve = "single"),
             shape = 1, alpha = 0.9) +
            xlab("Average  Section 3") +
            ylab("Geography Overall Percentile") +
            scale_x_continuous(limits = c(0, 30)) +
            scale_y_continuous(limits = c(0, 1)) +
            labs(color = "EoIs")




bscols(
  widths = c(8),
ggplotly(p, tooltip="text") %>%
      config(displaylogo = FALSE, 
             toImageButtonOptions = list(
               format = "png",
               filename = paste0("Section3"),
               width = 600,
               height = 600
             ),
             modeBarButtonsToRemove = c(
               'sendDataToCloud',
               'select2d',
               'autoScale2d',
               'lasso2d',
               'zoomIn2d',
               'zoomOut2d',
               'pan2d'
             )) %>%
      layout(autosize = TRUE, margin = list(t = 50))
)
```

***
# [Overview of Individual EoIs]{.ul}{.ul}


```{r echo = FALSE}

fullData <- readxl::read_xlsx("docs/fulldataTranslated.xlsx")
full_Data <- SharedData$new(fullData[c(1,4:7)])

bscols(
  widths = c(3, 9),
  list(
    filter_checkbox("Geography", "Geography", full_Data, ~Geography),
    filter_select("EoI", "EoI Number", full_Data, ~EoI)
  ),
  reactable(full_Data,
            columns = list(
              EoI = colDef(html = TRUE, cell = function(value, index) {
              # Render as a link
              url <- paste0("report.", value,".html")
              htmltools::tags$a(href = url, target = "_blank", as.character(value))
            })),
            showPageSizeOptions = TRUE, pageSizeOptions = c(5, 10, 25, 50), defaultPageSize = 5,
            highlight = TRUE,
            striped = TRUE)

)
```
