---
title: "Overview of EoI Reviews by TRC"
output:
  html_document:
    df_print: paged
  flexdashboard::flex_dashboard:
    orientation: rows
    social: menu
    source_code: embed
---
<style type="text/css">
.main-container {
  max-width: 1800px;
  margin-left: auto;
  margin-right: auto;
}
</style>

```{r setup, include=FALSE}
library(ggplot2)
library(crosstalk)
library(reactable)
library(plotly)
library(plyr)
library(flexdashboard)
library(htmltools)
# Make some noisily increasing data


```

-----------------------------------------------------------------------
### Summary Data of all reviews, aggregated by EoI
##### Use the controls on the left to subset the summary table and plot that follows.

```{r echo = FALSE}

summaryStats <- read.csv("summaryStats_Round.csv")
data <- SharedData$new(summaryStats)

bscols(
  widths = c(3, 9),
  list(
    filter_checkbox("Geography", "Geography", data, ~Geography),
    filter_slider("average", "Average", data, ~Average, width = "100%"),
    filter_select("EoI", "EoI Number", data, ~EoI)
  ),
  reactable(data, 
            columns = list(
    EoI = colDef(minWidth = 75),
    Geography = colDef(minWidth = 115),
    nReviews = colDef(minWidth = 85, name = "# of Reviews", html = TRUE, align = "left", header = JS("
      function(colInfo) {
        return colInfo.column.name
      }
    ")),
    Average = colDef(minWidth = 85),
    Avg_Sec_1 = colDef(minWidth = 85, name = "Average Section 1", html = TRUE, align = "left", header = JS("
      function(colInfo) {
        return colInfo.column.name
      }
    ")),
    Avg_Sec_2 = colDef(minWidth = 85, name = "Average Section 2", html = TRUE, align = "left", header = JS("
      function(colInfo) {
        return colInfo.column.name
      }
    ")),
    Avg_Sec_3 = colDef(minWidth = 85, name = "Average Section 3", html = TRUE, align = "left", header = JS("
      function(colInfo) {
        return colInfo.column.name
      }
    ")),
    Total = colDef(minWidth = 60),
    Min = colDef(minWidth = 60),
    Max = colDef(minWidth = 60),
    Range = colDef(minWidth = 60),
    Geog_Percentile = colDef(minWidth = 85, name = "Geog. Percentile", html = TRUE, align = "left", header = JS("
      function(colInfo) {
        return colInfo.column.name + '<div style=\"color: #999\">(%)</div>'
      }
    ")),
    Geog_Rank = colDef(minWidth = 75, name = "Geog. Rank", html = TRUE, align = "left", header = JS("
      function(colInfo) {
        return colInfo.column.name
      }
    ")),
    Overall_Rank = colDef(minWidth = 75, name = "Overall Rank", html = TRUE, align = "left", header = JS("
      function(colInfo) {
        return colInfo.column.name
      }
    ")),
    Overall_Percentile = colDef(minWidth = 85, name = "Overall Percentile", html = TRUE, align = "left", header = JS("
      function(colInfo) {
        return colInfo.column.name + '<div style=\"color: #999\">(%)</div>'
      }
    "))),
    showPageSizeOptions = TRUE, pageSizeOptions = c(5, 10, 25), defaultPageSize = 5,
    defaultSorted = list(Average = "desc"),
            highlight = TRUE,
            striped = TRUE)

)
```

### Performance of EoIs - Percentile by Average Total Score

```{r echo = FALSE}
p <- ggplot(data, aes(x=Average, y=Geog_Percentile, color = Geography, text=paste0("EoI: ", EoI,
                                                                                  "<br>",
                                                                                  "Geography: ", Geography,
                                                                                  "<br>",
                                                                                  "Average: ", Average,
                                                                                  "<br>",
                                                                                  "Geog. Percentile: ", Geog_Percentile)),
            group = Geography) +
            geom_point(shape=1) +
            xlab("Average Total Score") +
            ylab("Geography Percentile") +
            scale_x_continuous(limits = c(0, 100)) +
            scale_y_continuous(limits = c(0, 1))





bscols(
  widths = c(8),
ggplotly(p, tooltip="text")
)
```


### Performance of EoIs - Percentile by Average Score (Section 1)

```{r echo = FALSE}


p <- ggplot(data, aes(x=Avg_Sec_1, y=Geog_Percentile, color = Geography, text=paste0("EoI: ", EoI,
                                                                                  "<br>",
                                                                                  "Geography: ", Geography,
                                                                                  "<br>",
                                                                                  "Average: ", Average,
                                                                                  "<br>",
                                                                                  "Geog. Percentile: ", Geog_Percentile)), group = EoI) +
            geom_point(shape=1) +
  xlab("Average Section 1") +
  ylab("Geography Percentile") +
  scale_x_continuous(limits = c(0, 30)) +
  scale_y_continuous(limits = c(0, 1))




bscols(
  widths = c(8),
ggplotly(p, tooltip="text")
)
```

### Performance of EoIs - Percentile by Average Score (Section 2)

```{r echo = FALSE}


p <- ggplot(data, aes(x=Avg_Sec_2, y=Geog_Percentile, color = Geography, text=paste0("EoI: ", EoI,
                                                                                  "<br>",
                                                                                  "Geography: ", Geography,
                                                                                  "<br>",
                                                                                  "Average: ", Average,
                                                                                  "<br>",
                                                                                  "Geog. Percentile: ", Geog_Percentile)), group = EoI) +
            geom_point(shape=1) +
  xlab("Average Section 2") +
  ylab("Geography Percentile") +
  scale_x_continuous(limits = c(0, 40)) +
  scale_y_continuous(limits = c(0, 1))




bscols(
  widths = c(8),
ggplotly(p, tooltip="text")
)
```

### Performance of EoIs - Percentile by Average Score (Section 3)

```{r echo = FALSE}



p <- ggplot(data, aes(x=Avg_Sec_3, y=Geog_Percentile, color = Geography, text=paste0("EoI: ", EoI,
                                                                                  "<br>",
                                                                                  "Geography: ", Geography,
                                                                                  "<br>",
                                                                                  "Average: ", Average,
                                                                                  "<br>",
                                                                                  "Geog. Percentile: ", Geog_Percentile)), group = EoI) +
            geom_point(shape=1) +
  xlab("Average Section 3") +
  ylab("Geography Percentile") +
  scale_x_continuous(limits = c(0, 30)) +
  scale_y_continuous(limits = c(0, 1))




bscols(
  widths = c(8),
ggplotly(p, tooltip="text")
)
```

***
# [Overview of Individual EoIs]{.ul}{.ul}


```{r echo = FALSE}

fullData <- readxl::read_xlsx("fulldata.xlsx")
full_Data <- SharedData$new(fullData[c(1,4:7)])

bscols(
  widths = c(3, 9),
  list(
    filter_checkbox("Geography", "Geography", full_Data, ~Geography),
    filter_select("EoI", "EoI Number", full_Data, ~EoI)
  ),
  reactable(full_Data,
            showPageSizeOptions = TRUE, pageSizeOptions = c(5, 10, 25), defaultPageSize = 5,
            highlight = TRUE,
            striped = TRUE)

)
```
